Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex
Tocando el comentario relacionado con el number of commits per previous commit

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit. We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit. It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
Figure~\ref{fig:parent} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.

@@

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\label{fig:parent}       % Give a unique label
\caption{Information about the bug offered by Gerrit.}
\end{figure}

@@

We also studied the distribution of the number of previous commits for each bug. As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits. \grex{the number of commits that can be considered as previous is 1, followed by 2 commits. No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo? Que utilidad tiene?}\gema{Creo que era interesante saber como se distribuyen los causantes de los bugs en cada projecto y cuantos commits previos presentan los bugs report en cada projecto analizado, ademas cuantos mas commits previos, en ocasiones, es muy dificil saber quien es el responsable por tanto pense que podria haber algun patron en relacion con el numero de commits previos y cuantos de ellos son responsables, pero parece que esto no ocurre con la muestra que hemos analizado.}

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
\raisebox{1ex}{Neutron} & 11 & 3 & 2 & 2 & 0 \\[0ex]
\raisebox{1ex}{Horizon} & 39 & 8 & 3 & 2 & 4 \\[0ex]
\raisebox{1ex}{Nova} & 44 & 5 & 2 & 4 & 4 \\[0ex]
\raisebox{1ex}{Cinder} & 37 & 9 & 6 & 2 & 2\\[0ex]
\raisebox{1ex}{Total} & 131 & 25 & 13 & 10 & 10\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{ Distribution of the number of previous commits per bug report for each project.}
\label{tab:secondStage2}
\end{center}
\end{table*}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package including data sources, intermediate data and scripts that can be obtained at the following URL: \gema{Incluir la URL en la que pondre todos los datos y scripts utilizados para los datos.}

>>>>

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit. We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit. It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found.

@@

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\caption{Information about the bug offered by Gerrit.}
\label{fig:parentgerrit}       % Give a unique label
\end{figure}

@@

We also studied the distribution of the number of previous commits for each bug. This result will provide further insight into the bug-seeding nature; it offers as well an idea of the complexity of identifying the cause of a bug, as the more commits involved, the harder it is to identify the cause and understand it. As shown in Table~\ref{tab:secondStage2}, usually the number of commits that can be considered as previous is 1 (over 69\% of the cases), followed by 2 commits (13\%). In around 10\% of the cases, 3 or more commits are involved.

% the number of commits that can be considered as previous is 1, followed by 2 commits. \grex{the number of commits that can be considered as previous is 1, followed by 2 commits. No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo? Que utilidad tiene?}\gema{Creo que era interesante saber como se distribuyen los causantes de los bugs en cada projecto y cuantos commits previos presentan los bugs report en cada projecto analizado, ademas cuantos mas commits previos, en ocasiones, es muy dificil saber quien es el responsable por tanto pense que podria haber algun patron en relacion con el numero de commits previos y cuantos de ellos son responsables, pero parece que esto no ocurre con la muestra que hemos analizado.}

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}& \multicolumn{1}{c}{commit}\\\hline
\raisebox{1ex}{Neutron} & 11 & 3 & 2 & 2 & 0 \\[0ex]
\raisebox{1ex}{Horizon} & 39 & 8 & 3 & 2 & 4 \\[0ex]
\raisebox{1ex}{Nova} & 44 & 5 & 2 & 4 & 4 \\[0ex]
\raisebox{1ex}{Cinder} & 37 & 9 & 6 & 2 & 2\\[0ex]
\raisebox{1ex}{Total} & 131 & 25 & 13 & 10 & 10\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{ Distribution of the number of commits that can be considered as the previous commit per bug report for each project.}
\label{tab:secondStage2}
\end{center}
\end{table*}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gsyc.urjc.es/~grex/repro/2016-msr-prevcommit}} including data sources, intermediate data and scripts that can be obtained.
